### 2014-06-28 Choosing R3 Relations.tex
adding_6_additional_relations

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newcommand\tri{s_3^{-1}}
\newcommand\tr{s_3}
\newcommand\twi{s_2^{-1}}
\newcommand\tw{s_2}
\newcommand\oni{s_1^{-1}}
\newcommand\on{s_1}

@@

\begin{rem}
I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$
\end{rem}

\begin{lem}
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

>>>>

\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newcommand\tri{s_3^{-1}}
\newcommand\tr{s_3}
\newcommand\twi{s_2^{-1}}
\newcommand\tw{s_2}
\newcommand\oni{s_1^{-1}}
\newcommand\on{s_1}

@@

\begin{rem}
\label{even_more_relations}
I am proposing to add the following relations whever we have the situation

$\xymatrix{a \ar[r]^2 & b \ar[r]^1 & c},$ or $\xymatrix{a \ar[r]^1 & b \ar[r]^2 & c}:$

Include $s_is_{i+1}^2 = s_{i+1}^2s_i,$ and $s_is_{i-1}^2 = s_{i-1}^2s_i,$ for all $i = 1,2,3.$ I believe these mutate correctly, as in cases b,c,d in Barot-Marsh. Note that in the above diagrams, it is fine if we have a 2 edges from a to c or c to a.
\end{rem}

\begin{lem} (4.2 Analog)
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw$ from ~\ref{even_more_relations}, the two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}
